A Data-Driven Framework for Neural Field Modelling

### 2010-11-15 ltx/first_order_framework/LaTeX_Manuscript.tex
added reference to the work of Freeman to the discussion, spatial freq analysis

The frequency analysis specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics. Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing. In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data. This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes~\cite{Brinkmann2009}.

>>>>

The frequency analysis specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics. As pointed out in numerous publications by Freeman and colleagues (see \cite{Freeman1987} for example), a detailed description of the spatial properties of responses to stimuli is essential in understanding cortical dynamics. Importantly, the spatial frequency analysis tools presented in this paper can be used to design electrophysiological recording systems to avoid spatial aliasing, ensuring the essential spatial properties can be recovered. In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data. This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes~\cite{Brinkmann2009}.
